---
title: "Parasite energetics MS"
author: "Rita Grunbreg"
date: "5/19/2020"
output: html_document
---


```{r setup,  results='hide', message=FALSE, warning=FALSE}
rm(list = ls())  # clear Rs brain 
library(readr)   # read csv file in - easy
library(tidyr)   # tidying data
library(plyr)    # dependency 
library(dplyr)   # manipulating df
library(tidyverse)
library(ggplot2) # graphing
library(ggpubr)  # nice package for figures
library(effects) #visualize partial residuals 
################################################################################################
```


Four datasets are providing as .csv files.

Data S1. 'DataS1.parasite_community_abundance_data' This is a .csv file containing data pertaining to Figure 1. In Figure 1 plotted are the partial residuals of the linear model: np ~ avg_alpha + mh_alph_no_temp Note. Data S1 is filtered by absolute maximum community abundance; see Table S2 for comparison of model coeffs.

Data S2. 'DataS2.parasite_community_flux_data' This is a .csv file containing data pertaining to Figure 2. In Figure 2 plotted is parasite_flux ~ mh_alpha Note. Data S2 is filtered by absolute maximum community flux; see Table S3 for comparison of model coeffs.

Data S3. 'DataS3.energy_flux_ecosystem' This is a .csv file containing data pertaining to figure 3. In Figure 3A plotted are log_parasite_flux ~ log _host_flux + river In Figure 3B plotted are log_parasite_biomass ~ log_host_biomass +river

Data S4. 'DataS4.platyhelminthes_scaling' This is a .csv file containing data used to estimate platyhelminthe metabolic scaling parameters given in Table 1, further details are provided in Appendix 1.

```{r upload datasets,  results='hide', message=FALSE, warning=FALSE}
#setwd()
DataS1_parasite_community_abudance <- read_csv("C:/Users/grunberg/Desktop/data/DataS1.parasite_community_abudance.csv")
DataS2_parasite_community_flux <- read_csv("C:/Users/grunberg/Desktop/data/DataS2.parasite_community_flux.csv")
DataS3_energy_flux_ecosystem <- read_csv("C:/Users/grunberg/Desktop/data/DataS3.energy_flux_ecosystem.csv")

rita_theme <-  theme_classic(base_size = 13)+
  theme(legend.title = element_text(size=9, face="bold"),
        legend.text = element_text(size=8),
        axis.line = element_line(colour = 'black', size = 0.75),
        axis.ticks = element_line(colour = "black", size = 0.75),
        axis.text.x = element_text(size=10,  colour = "black"), 
        axis.text.y = element_text(size=10,  colour = "black"), # bold
        axis.title.y = element_text(size=12, colour = "black")
  )
```

Metadata for data S1 and S2:
Column_headers. 

host_species: genus and species of host taxa 
code: unique identifier of host individual used in the analysis 
parasite_flux:  unit watts; temperature corrected parasite community flux following equation 6 in the main text; parasite flux = [(a*parasite body mass (kg) ^b)* exp((E_parasite/0.0000862)*(-((Temp_O+273.15)^-1) + ((Temp+273.15)^-1))))] * parasite abundance) and summed across all parasite species, where a = phylum specific normalization constant from table 1 in maint text and b = phylum specific scaling exponenet from table 1.  
mh_alpha: unit watts; temperature corrected host metabolic rate following equation 5 in the maint text; host metabolic rate = (a * host body mass (kg) ^ b) * exp((E_host/0.0000862)*(-((Temp_O+273.15)^-1) + ((Temp+273.15)^-1))))
mh_alpha_no_temp: unit watts; host metabolic rate following equation 5 in the maint text; host metabolic rate = (a * host body mass (kg) ^ b) 
mh: units grams; host body mass 
np: total parasite abundance, which is all parasite individuals within a host 
n: number of hosts dissected; using a min. of 15 individuals per host species
avg_alpha: unit watts; mean energy usage within a parasite community see main text for calculation (note this is not temp corrected)
host_taxon: host taxonomic group, pertains to metabolic scaling parameters in table 1
Temp_O: units celsius; environmental temperature during collection period (notes needs to transforemd to kelvin for temperature correction) 
Data_source: where the data came from, new data= unpublished data first used in this manuscript 

Metadata for S3.:
Column_headers.

river: name of river ecosystem; Passaic, Raritan, Mullica
season: seaon fall, winter, spring, summer 
plot: site within river ecosystem 
log_parasite_flux: units watts/m^2; log10 transformed parasite community flux within a sample
log_host_flux: units watts/m^2; log10 transformed host community flux within a sample 
log_parasite_biomass: units g/m^2; log10 transformed parasite biomass density within a sample 
log_host_biomass: units g/m^2; log10 transformed host biomass density within a sample 

Metadata for S4:
Column_headers.

species: parasite species; genus species
stage: parasite lifecycle stage; adult, larvae, sporocyst, redia 
Temperature C: temperature at which metabolic rate was taken in degrees celsius 
Body mass in original units: body mass of parasite in orignal units from study
Mass original units: units of mass  in study
Mean Respiration Rate in original units: metabolic rate in orignal units from study
respiration_units: units of metabolic rate in study
Notes on conversion: all conversions used
ln(body mass) (kg): units kg; natural log transformed body mass in wet weight 
ln(metabolic rate) (Watts): units watts;  natural log transformed metabolic rate
Source:	citation of study
Host type: host used in the study given as genus species/'free-living' indicates free living larval stage used 

```{r check headers of data}
head(DataS1_parasite_community_abudance)
head(DataS2_parasite_community_flux)
head(DataS3_energy_flux_ecosystem)
```

Testing prediction  1 from MS. Maximum parasite community abundance increases with host metabolic rate as a power law with an exponent of 1, decreases with average parasite energy use as a power law with an exponent of negative 1, and is invariant with respect to temperature (Eqn 3 from MS). 

Note: when including temperature in mod1.weighted.temp, we must use a natural log transformation, and all models are weighted by host sample size

```{r community abundance}
mod1.weighted <-lm(log10(np) ~ log10(mh_alpha_no_temp) + log10(avg_alpha) , weights=n, data= DataS1_parasite_community_abudance)
mod1.weighted.temp <-lm(log(np) ~ log(mh_alpha_no_temp)+ log(avg_alpha) + log(arhen_temp), weights=n, data= mutate(DataS1_parasite_community_abudance, arhen_temp = 1/((Temp_O+273)*8.62e-5)))
summary(mod1.weighted )
summary(mod1.weighted.temp)

########################################################################
#log10 transform data
DataS1_parasite_community_abudance <-DataS1_parasite_community_abudance %>%
  mutate(log_mh = log10(mh_alpha_no_temp),
         log_avg_parasite = log10(avg_alpha), 
         log_np = log10(np))

#Drop the temp for the final model
mod1.final <-lm(log_np ~ log_mh + log_avg_parasite , weights=n, data= DataS1_parasite_community_abudance)
summary(mod1.final)
confint(mod1.final)

```
This creates partial residuals for figure 1 in the manuscript 

```{r partial residuals}
closest <- function(x, x0) apply(outer(x, x0, FUN=function(x, x0) abs(x - x0)), 1, which.min)

partial.mod1.hostmass <- effect('log_mh', mod1.final, partial.residuals=T)
plot(partial.mod1.hostmass)

hostmass.fit <- unlist(partial.mod1.hostmass$x.all)
trans <- I
x <- data.frame(lower = partial.mod1.hostmass$lower, 
                upper = partial.mod1.hostmass$upper, 
                fit =partial.mod1.hostmass$fit, 
                log_mh = partial.mod1.hostmass$x$log_mh)
xy <- data.frame(x = hostmass.fit,
                 np_partial_mp = x$fit[closest(trans(hostmass.fit), x$log_mh)] + partial.mod1.hostmass$residuals)

######################
partial.mod1.parasitemass <- effect('log_avg_parasite', mod1.final, partial.residuals=T)
plot(partial.mod1.parasitemass)

parasitemass.fit <- unlist(partial.mod1.parasitemass$x.all)
trans <- I
x.2 <- data.frame(lower = partial.mod1.parasitemass$lower, 
                upper = partial.mod1.parasitemass$upper, 
                fit =partial.mod1.parasitemass$fit, 
                log_avg_parasite = partial.mod1.parasitemass$x$log_avg_parasite)
xy.2 <- data.frame(x = parasitemass.fit,
                   np_partial_mh = x.2$fit[closest(trans(parasitemass.fit), x.2$log_avg_parasite)] + partial.mod1.parasitemass$residuals)

DataS1_parasite_community_abudance_mh <- cbind(DataS1_parasite_community_abudance, xy)
DataS1_parasite_community_abudance_avgp <- cbind(DataS1_parasite_community_abudance, xy.2)

```
This generates figure 1 from the manuscript. Here, we plot the partial residuals of the model describing parasite abundance ~ host metabolic rate + average parasite energy use across hosts species 

```{r graphics community abundance, echo=FALSE}

mh_plot <- ggplot(data=x,
                  aes(x=log_mh, y = fit))+
  geom_line(size = 1) + 
  geom_ribbon(aes(ymin=x$lower, ymax=x$upper), linetype=2, alpha=0.1)+
  geom_point(data=DataS1_parasite_community_abudance_mh, 
             aes(x= x, y = np_partial_mp, fill = host_taxon), shape = 21, size = 2, stroke = 0.75) + 
  labs(y=expression(log["10"]~resid.~community~abun.),
       x=expression(log["10"]~host~metabolic~rate~(watts)))+ 
  rita_theme+
  theme(legend.title = element_blank(), legend.position = "none")+
  scale_fill_manual(values = c('#ffffcc','#a1dab4','#41b6c4','#225ea8'))
mh_plot

mp_plot <- ggplot(data=x.2,
                  aes(x=log_avg_parasite, y = fit))+
  geom_ribbon(aes(ymin=x.2$lower, ymax=x.2$upper), linetype=2, alpha=0.1)+
  geom_line(size = 1) + 
  geom_point(data=DataS1_parasite_community_abudance_avgp, 
             aes(x= x, y = np_partial_mh, fill = host_taxon), shape = 21, size = 2, stroke = 0.75) + 
  labs(y=expression(log["10"]~resid.~community~abun.),
       x=expression(log["10"]~mean~parasite~energy~use~(watts)))+ 
  rita_theme+
 guides(fill=guide_legend("",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"), color=FALSE) +
  theme(legend.position = c(0.87,0.87)) +
  scale_fill_manual(values = c('#ffffcc','#a1dab4','#41b6c4','#225ea8'))

#jpeg(file="figure1.jpeg", width = 180, height = 180, units = 'mm', res = 300)
ggarrange(mp_plot, mh_plot, nrow=1, ncol=2, labels = 'AUTO')
#dev.off()


```

Following codes to test prediction 2: the energy flowing through parasite communities is directly proportional to host metabolic rate. 

```{r community flux}
mod2 <- lm(log10(parasite_flux)~ log10(mh_alpha), weights=n,data= DataS2_parasite_community_flux)
summary(mod2)
confint(mod2)

#exp intercept of the model
10^(mod2$coefficients[1])

# fraction of energy being used by parasites
1-mod2$coefficients[2]
```

We also evaluated whether the relationship between parasite infracommunity energy flux (F_p) and host metabolic rate (R_h) reflects these variables’ respective relationships with host body mass (M_h). To do so, we examined the relationship between the residuals of the relationship of log10⁡(F_p ) to log10⁡(M_h ) and the residuals of the relationship of log10⁡(R_h ) to log10⁡(M_h ). 

```{r body size residual analysis}
### residuals analysis suggested by reviewer #1
mod2.1 <- lm(log10(parasite_flux)~ log10(mh), weights = n, data=DataS2_parasite_community_flux)
mod2.2 <- lm(log10(mh_alpha)~ log10(mh), weights = n, data=DataS2_parasite_community_flux)

DataS2_parasite_community_flux$pflux_mass_resid <- residuals(mod2.1)
DataS2_parasite_community_flux$mhalpha_mass_resid <- residuals(mod2.2)

mod2.resid<- lm(pflux_mass_resid~mhalpha_mass_resid, weights = n, data=DataS2_parasite_community_flux)
summary(mod2.resid)
```

Generates figure 2 of the manuscrip that shows the scaling of host and parasite energy flux

```{r graphic community abundance, echo=FALSE}
h1<-ggplot(DataS2_parasite_community_flux, aes(x=log10(mh_alpha), y = log10(parasite_flux)))+
  geom_smooth(method="lm", se=T, lty=1, alpha=0.2, color='black')+ 
  geom_point(pch=21, size = 2, aes(fill=host_taxon), stroke=0.75) + 
  scale_fill_manual(values = c('#ffffcc','#a1dab4','#41b6c4','#225ea8'))+
  xlab(bquote(~log[10]~'host metabolic rate (watts)'))+ 
  ylab(bquote(~log[10]~'parasite community flux (watts)'))+ 
  rita_theme+
  theme(legend.title = element_blank(),
        legend.text = element_text(size=8))+ guides(shape=FALSE)+ 
  theme(legend.position=c(0.17,0.85) #,
  )+
  guides(fill=guide_legend("",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                            default.unit="inch"))

#jpeg(file="figure2.jpeg", width = 90, height = 90, units = 'mm', res = 500)
h1
#dev.off()
```

Testing the third prediction of our manuscript. Parasite productivity across ecosystems scales with host producitivity.

Ecosystem-level scaling of parasite and host productivity, here fish productivity, were analysed using log-transformed biomass density and community flux data. Each observation in this analysis is the mean of a seasonal sample taken at a site within each of the three river ecosystem 

```{r formatting season}
DataS3_energy_flux_ecosystem$season<-gsub("Fall", "fall", DataS3_energy_flux_ecosystem$season)
DataS3_energy_flux_ecosystem$season<-gsub("Winter", "winter", DataS3_energy_flux_ecosystem$season)
DataS3_energy_flux_ecosystem$season<-gsub("Spring", "spring", DataS3_energy_flux_ecosystem$season)
DataS3_energy_flux_ecosystem$season<-gsub("Summer", "summer", DataS3_energy_flux_ecosystem$season)

```

Belows runs the host and parasite energy flow model for Figure 3
```{r energy_model}
fullinteraction_model <- lm(log_parasite_flux ~ log_host_flux * river, data=DataS3_energy_flux_ecosystem)
summary(fullinteraction_model)
anova(fullinteraction_model)

full_model <- lm(log_parasite_flux ~ log_host_flux + river, data=DataS3_energy_flux_ecosystem)
summary(full_model)
confint(full_model)

flux_model <- data.frame("flux density", 
                         full_model$coefficients[2], 
                         full_model$coefficients[1], 
                        (full_model$coefficients[1] + full_model$coefficients[3]),
                        (full_model$coefficients[1] + full_model$coefficients[4]),
                        summary(full_model)$r.squared, 
                        anova(full_model)$'Pr(>F)'[1]) 

colnames(flux_model) <- c("model", "slope", "Mullica", "Passaic", "Raritan","R2", "p_value")
flux_model
```
Generates graphic for Figure 3 in the manuscript 

```{r energy_graphic, echo=FALSE}
flux.pred <- data.frame(predict(full_model, interval = "confidence"))
DataS3_energy_flux_ecosystem$pred <- flux.pred$fit
DataS3_energy_flux_ecosystem$upper <- flux.pred$upr
DataS3_energy_flux_ecosystem$lower <- flux.pred$lwr

full_flux <-ggplot(DataS3_energy_flux_ecosystem, aes(x=log_host_flux, y=log_parasite_flux, group=river))+
  geom_ribbon(aes(ymin=DataS3_energy_flux_ecosystem$lower, ymax=DataS3_energy_flux_ecosystem$upper),  alpha=0.1)+
  geom_point( size = 2, aes(fill=river, shape=season)) + 
  scale_fill_manual(values =c('#f7f7f7','#969696','#252525')) +
  scale_shape_manual(values=c(21,22,23,24))+
  ylab(bquote(~log[10]~'parasite (watts/'~m^2*')'))+ 
  xlab(bquote(~log[10]~'host (watts/'~m^2*')'))+ 
  geom_line(aes(x=log_host_flux, y = pred, linetype=river, data=))+
  guides(color=FALSE, linetype=FALSE)+ 
  rita_theme+
 # theme_pubr()+
  theme(#legend.title = element_blank(),
        legend.text = element_text(size=8))+ 
  theme(legend.position=c(0.16,0.85))+
  guides(fill=guide_legend(title="Ecosystem",  keywidth=0.12,
                           keyheight=0.12, override.aes = list(shape=21),
                           default.unit="inch"),
         shape=guide_legend(title="Season",  keywidth=0.12,
                           keyheight=0.12, 
                           default.unit="inch")) 
full_flux
```

Below runs the host and parasite biomass density model for Figure 3

```{r biomass_model}
full_model_b1.interaciton <- lm(log_parasite_biomass ~ log_host_biomass * river, data=DataS3_energy_flux_ecosystem)
anova(full_model_b1.interaciton)


full_model_b1 <- lm(log_parasite_biomass ~ log_host_biomass + river, data=DataS3_energy_flux_ecosystem)
summary(full_model_b1)
confint(full_model_b1)

bio_model <- data.frame("biomass density", 
                        full_model_b1$coefficients[2], # slope
                        full_model_b1$coefficients[1], #intercept mullica
                        (full_model_b1$coefficients[1] + full_model_b1$coefficients[3]), # intercept passaic
                        (full_model_b1$coefficients[1] + full_model_b1$coefficients[4]), # intercept rariatn
                        summary(full_model_b1)$r.squared,
                        anova(full_model_b1)$'Pr(>F)'[1]
                        ) 

colnames(bio_model) <- c("model", "slope", "Mullica", "Passaic", "Raritan","R2", "p_value")
bio_model

```

Generates graphic for Figure 3

```{r biomass_graphic, echo=FALSE}
flux.pred.2 <- data.frame(predict(full_model_b1, interval = "confidence"))
DataS3_energy_flux_ecosystem$pred.2 <- flux.pred.2$fit
DataS3_energy_flux_ecosystem$upper.2 <- flux.pred.2$upr
DataS3_energy_flux_ecosystem$lower.2 <- flux.pred.2$lwr

full_biomass <- ggplot(DataS3_energy_flux_ecosystem, aes(x=log_host_biomass, y=log_parasite_biomass, group=river))+
  geom_ribbon(aes(ymin=DataS3_energy_flux_ecosystem$lower.2, ymax=DataS3_energy_flux_ecosystem$upper.2),  alpha=0.1)+
  geom_point( size = 2, aes(fill=river, shape=season)) + 
  scale_fill_manual(values =c('#f7f7f7','#969696','#252525')) +
  scale_shape_manual(values=c(21,22,23,24))+
  ylab(bquote(~log[10]~'parasite (g/'~m^2*')'))+ 
  xlab(bquote(~log[10]~'host (g/'~m^2*')'))+ 
  geom_line(aes(x=log_host_biomass, y = pred.2, linetype=river))+
  rita_theme+
  #theme_pubr()+
  guides(color=FALSE, fill=FALSE, linetype=FALSE, shape=FALSE)
full_biomass
```
Paneled graphic for Figure 3. 

```{r eco_graphic, echo=FALSE}
#jpeg(file="figure4.jpeg", width = 180, height = 90, units = 'mm', res = 500)
ggarrange(full_flux, full_biomass, labels = c("A", "B"))
#dev.off()

```
